Concurrent Programming with CXL

### 2020-06-25 book/paper.tex
Latest

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e} & two CXL values of the same type \\
\hline
\texttt{e != e} & two CXL values of the same type \\
\hline
\texttt{e < e} & any two CXL values \\
\hline
\texttt{e <= e} & any two CXL values \\
\hline
\texttt{e > e} & any two CXL values \\
\hline
\texttt{e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e in e} & first is any CXL value, second is set \\
\hline
\texttt{e not in e} & first is any CXL value, second is set \\
\hline
\texttt{e if e else e} & middle \texttt{e} must be a Boolean \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e} & a set \\
\hline
\texttt{max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{\&lv} & \texttt{lv} is an lvalue \\
\hline
\texttt{stop lv} & \texttt{lv} is an lvalue \\
\hline
\end{tabular}
\vspace{1em}

>>>>

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e}, \texttt{e != e} & two CXL values of the same type \\
\hline
\texttt{e < e, e <= e} & any two CXL values \\
\hline
\texttt{e > e, e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e [not] in e} & first is any CXL value, second is set \\
\hline
\texttt{e if e else e} & middle \texttt{e} must be a Boolean \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e, max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{\&lv} & \texttt{lv} is an lvalue \\
\hline
\texttt{stop lv} & \texttt{lv} is an lvalue \\
\hline
\end{tabular}
\vspace{1em}
